Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-30 Report/convergence_centralized.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem. The positive constant \me{c_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{m > 0} be the constant of strong convexity of \eqn{f} with \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} as in \cite{scutari-1}. Therefore, by using the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step \cite{yang_yang,scutari-1}. The quadratic term in \eqref{mod_obj} includes the earlier solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, obtained by solving \eqref{eqn-9} or \eqref{eqn-mse-2} in the \eqn{\ith{(k-1)}} \ac{SCA} step.}

@@

Thus the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing. \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique. Using this and the fact that the sequence of objectives is nonincreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.  However, note that the limit point need not be a stationary point of \eqref{con} since the receive beamformers \eqn{\my} have been fixed.}

@@

Once \me{\iter{\mx}{\ast}{i}} is found for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}. However, after fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}. Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.

@@

\review{Using the above discussions, the monotonicity of the objective seqeunce is guaranteed in each \ac{AO} and \ac{SCA} updates. However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some constant \eqn{m > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
\end{IEEEeqnarray}
since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.

@@

Now, to prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications. Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}, therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
\end{equation}
The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
\begin{equation} \label{rhs_equiv}
\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
\end{equation}
Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}. By using \cite[Th. 2 and 11]{scutari_1} or \cite[Prop. 3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the original nonconvex problem in \eqref{con}.}

>>>>

\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity of \eqn{f} with \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} as in \cite{scutari-1}. Therefore, by using the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step \cite{yang_yang,scutari-1}. The quadratic term in \eqref{mod_obj} includes the earlier solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, obtained by solving \eqref{eqn-9} or \eqref{eqn-mse-2} in the \eqn{\ith{(k-1)}} \ac{SCA} step.}

@@

Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing. \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique. Using this and the fact that the sequence of objectives is nonincreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.  However, note that the limit point need not be a stationary point of \eqref{con}, since the receive equalizers \eqn{\my} have been fixed.}

@@

Once \me{\iter{\mx}{\ast}{i}} is found for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}. However, after fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}. Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively. Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration. The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above. \footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.

@@

\review{Using the above discussions, the monotonicity of the objective sequence is guaranteed in each \ac{AO} and \ac{SCA} updates. However, to ensure the strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{c}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
\end{IEEEeqnarray}
since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.

@@

To prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications. Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}. Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
\end{equation}
The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}. Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfy \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given as
\begin{equation} \label{rhs_equiv}
\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
\end{equation}
Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}. By using \cite[Thms. 2 and 11]{scutari_1} or \cite[Prop. 3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the problem in \eqref{con}.}

### 2015-07-30 Report/convergence_distributed.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

\review{To show the convergence of \ac{ADMM}, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing the problem as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size. If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments in Appendix \ref{sec-3.5}. }

@@

However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence. \review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, note that the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update. Due to the above said reasons, the iterative scheme outlined in Algorithm \ref{algo-4} cannot find a fixed point to ensure the convergence of the beamformer iterates.}

>>>>

\review{To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size. If both the primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments as in Appendix \ref{sec-3.5}. }

@@

However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus, achieving improved speed of convergence. \review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update. Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot find a fixed point to ensure the convergence of the beamformer iterates.}
